Non-crop features influence the abundance and timing of beneficial arthropod abundance

### 2020-08-13 manuscript/manuscript_outline.Rmd
Added Nakagawa R2 estimates

@@

_Phalangium opilio_ activity density responded to grasslands and wetlands.
_P. opilio_ avoids heavily grazed areas, possibly due to low humidity, but is active in most other habitat types [@sajna2011].
In particular, it is largely found in human-altered landscapes with a large proportion of farming [@muster2014; @vandepoel2015Msc].
Our results show that _P. opilio_ migrated into pastures.
It is also found in large numbers at the edges of forests, and may migrate from forests into farmlands [@vandepoel2015Msc].
We found the opposite pattern (albeit weakly): _P. opilio_ appears to migrate into forests.

>>>>

#Calculate marginal and conditional R2 (Nakagawa and Schielzeth 2013)
r2Nakagawa <- sapply(list(PteMelMod=PteMelMod,ParDisMod=ParDisMod,ParMoeMod=ParMoeMod,OpilioMod=OpilioMod), function(modList){
  with(modList,getR2Terms(mod3,intVal=exp(mod1$coefficients[[1]]),thetaVal=mod1$family$getTheta(TRUE)))
})

@@

_Phalangium opilio_ activity density responded to grasslands and wetlands as well as trees and shrubs, but habitat
Grasslands and wetlands acted

_P. opilio_ avoids heavily grazed areas, possibly due to low humidity, but is active in most other habitat types [@sajna2011].
In particular, it is largely found in human-altered landscapes with a large proportion of farming [@muster2014; @vandepoel2015Msc].
It is also found in large numbers at the edges of forests, and may migrate from forests into farmlands [@vandepoel2015Msc].
We found the opposite pattern (albeit weakly): _P. opilio_ appears to migrate into forests.
